Outline

### 2022-02-01 text/main.Rmd
figure sizes

### 1. Underwater visual census database
\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019]. This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans. Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019]. The database only includes transects on the outer reef slope and with a hard reef bottom. Transects were carried out at a constant depth, parallel to the reef crest. We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm (to minimize the bias related to the identification of small individuals), and rare species for which less than 20 individuals were recorded across all transects. The dataset then included 1,110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html). Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014]. All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).

### 2. Quantification of functions
\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN m^-2^ day^-1^), phosphorus excretion rate (gP m^-2^ day^-1^), production of biomass through growth (gC m^-2^ day^-1^), herbivory, (i.e. ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e. ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front]. These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g. daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020].
This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020]. We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods). We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to obtain the contribution of each individual to each function in each transect. Finally, we summarized functions at the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area. Each function is thus exressed as dry mass (of C, N, or P) per day per square meter. We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020. To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al. (2020) [@Parravicini2020]. Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on Expert opinion [@Mouillot2014; @Parravicini2020] (Fig. S5). Both the herbivory and piscivory rates match the Expert opinion trophic guild classifications.
Finally, we estimated multifunction, i.e. one measure that combines all five functions by taking the geometric average of the five functions (normalized to a range between zero and 100). We used the geometric mean because functions are dependent on each other and vary by several orders of magnitude.

### 3. Community structure variables
We quantified a set of variables that characterize fish community structure. These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020]. Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect. The total length is based on visual estimations by divers. The immaturity is quantified using the following formula:
<!-- \begin{equation} -->
	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
<!-- 	\label{imm} -->
<!-- \end{equation} -->
where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i. Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual. Finally, trophic level was extracted from Fishbase [@Froese2018].

@@

We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function. For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004].\par

@@

Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004]. Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature. We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:

@@

All Bayesian models were fitted using the R package *brms* [@Burkner2017], which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017]. The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up. Thus, a total of 4,000 draws were used to estimate posterior distributions. The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig S2).

>>>>

### 1. Underwater visual census database
\noindent We used a published global database of reef fish abundances and sizes collected along belt transects [@Barneche2019] . This database encompasses 9,118 transects across 585 sites (within 98 localities) in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, and Western Atlantic Oceans. Sites are defined as small islands or stretches of continuous reefs in larger coastlines and localities encompass sites that belong to the same biogeographic sub-provinces [see @Barneche2019] . The database only includes transects on the outer reef slope and with a hard reef bottom. Transects were carried out at a constant depth, parallel to the reef crest. We discarded the species inside families for which we did not have body stoichiometry data, individuals that were smaller than 7cm (to minimize the bias related to the identification of small individuals), and rare species for which less than 20 individuals were recorded across all transects. The dataset then included 1,110 species belonging to 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).
Sea surface temperature (SST) for each site was obtained from daily time‐series data from the National Oceanicand Atmospheric Administration (NOAA) covering a 5‐year period (°C; 0.25° resolution) (@Reynolds2007; available from https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oiSST.v2.highres.html). Further, for each transect, we calculated species richness and estimated total standing stock biomass of fishes by using Bayesian length-weight relationships available from Fishbase [@Froese2014] . All data processing and analyses were performed in the software program R (version 4.0.2; R core team 2020).

### 2. Quantification of functions
\noindent For each transect, we estimated five key process-based functions mediated by fishes: nitrogen excretion rate (gN m^-2^ day^-1^), phosphorus excretion rate (gP m^-2^ day^-1^), production of biomass through growth (gC m^-2^ day^-1^), herbivory, (i.e. ingestion rate of macrophytes (gC m^-2^ day^-1^)), and piscivory (i.e. ingestion rate of fishes ( m^-2^ day^-1^)) [@Brandl2019front] . These five functions were estimated for each transect using individual-based bioenergetic models predicting fluxes of carbon (C), nitrogen (N), and phosphorus (P) (e.g. daily C intake rates, N and P excretion rates, and growth rates) [@Schiettekatte2020] .
This bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020] . We quantified the input parameters, including elements of metabolism, growth, and diet and body stoichiometry, for all 1110 species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (see supplementary methods). We then ran a unique bioenergetic model for each combination of species identity, body size, and sea surface temperature (n = 30668) to obtain the contribution of each individual to each function in each transect. Finally, we summarized functions at the community level by summing up all individual contributions inside a transect and deviding the sum by the surface area. Each function is thus exressed as dry mass (of C, N, or P) per day per square meter. We note that N excretion, P excretion, and biomass production include contributions of all fishes, whereas herbivory and piscivory are carried out by a subset of the community, with respect to their trophic guild as defined by @Parravicini2020. To reduce the occurrence of misclassification of herbivores and piscivores, we categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds presented by Parravicini et al. (2020) [@Parravicini2020] . Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on Expert opinion [@Mouillot2014; @Parravicini2020]  (Fig. S5). Both the herbivory and piscivory rates match the Expert opinion trophic guild classifications.
Finally, we estimated multifunction, i.e. one measure that combines all five functions by taking the geometric average of the five functions (normalized to a range between zero and 100). We used the geometric mean because functions are dependent on each other and vary by several orders of magnitude.

### 3. Community structure variables
We quantified a set of variables that characterize fish community structure. These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020] . Specifically, we calculated the 2.5%, 50%, and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect. The total length is based on visual estimations by divers. The immaturity is quantified using the following formula:
<!-- \begin{equation} -->
	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
<!-- 	\label{imm} -->
<!-- \end{equation} -->
where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i. Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual. Finally, trophic level was extracted from Fishbase [@Froese2018] .

@@

We fitted three multivariate Bayesian models with all five functions to (1) predict functions on the locality level to create a maps of functions, (2) investigate the effects of bioimass and SST, and the correlations among functions independent of biomass and SST, and (3) estimate the effects of the community structure on each function. For each model, functions were log-transformed to ensure the normal distribution of residuals and an allometric relationship with biomass, which is hypothesized by metabolic theory [@Brown2004] .\par

@@

Second, we ran a mixed-effect model to investigate the effects of biomass and SST on all functions and the correlations among functions (independent of biomass and SST).
The standing stock biomass of communities is positively related to all functions because of the additive nature of the quantification and metabolic theory [@Brown2004] . Furthermore, because of the known relationship between temperature and parameters related to growth and respiration (see supplementary methods), functions are expected to be affected by temperature. We thus fitted a multivariate Bayesian mixed-effect model using transect-level log-transformed functions that included random effects for sites and localities:

@@

All Bayesian models were fitted using the R package *brms* [@Burkner2017] , which uses Stan, a C++ package to perform full Bayesian inference [@Carpenter2017] . The posterior distributions of model parameters were estimated using Hamiltonian Monte Carlo (HMC) methods by using four chains of 2,000 samples, including 1,000 samples as a warm‐up. Thus, a total of 4,000 draws were used to estimate posterior distributions. The convergence and fit of the models were verified by examining the Rhat, parameter trace plots, and posterior prediction plots (Fig S2).
